\documentclass[11pt,modernstyle]{thesis}
\usepackage{graphicx}
%\usepackage[maxbibnames=1, style=phys, backend=bibtex]{biblatex}
%\addbibresource{myref.bib}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{setspace}
\usepackage{cancel}

\title{Search for supersymmetry in diphoton final states with the CMS detector}
\author{Matthew Lawrence Joyce}

\doublespacing
\begin{document}
	\maketitle
	\begin{abstract}
		This document presents a search for new physics having final states with two photons and missing transvers energy.  Data from proton-proton collisions with a center of mass energy of $\sqrt{s}=13$ TeV were used.  Said data was collected at the CERN LHC in the years 2016-2018 and make up a total integrated luminosity of 137 fb$^{-1}$.  Interpretation of the results was done in the context of gauge mediated supersymmetry breaking or more specifically the T5gg and T6gg simplified models.  The T5gg model is one where gluino pairs are produced which yield neutralinos which then each decay into a gravitino and a photon.  In the T6Wg model squark pairs are produced which yield neutralinos and then, as in the T5Wgg, each neutralino decays to a gravitino and a photon.  The gravitino would escape the detector undetected and therefore lead to a final state with missing transverse energy and two photons.  No significant excess was observed above the expected standard model backgrounds.  Lower limits were placed on the masses of the squarks and gluinos in the context of gauge mediated supersymmetry breaking.  Models with squark masses below -----  TeV were excluded at a 95\% confidence level as were models with gluino masses below ---- TeV.
	\end{abstract}
	\tableofcontents
	\listoffigures
	\listoftables
	\begin{linenumbers}	
	\input{Chapters/StandardModel}
	\input{Chapters/SUSY}
	\input{Chapters/LHC}
	\input{Chapters/CMS}
	\input{Chapters/TriggerSystem}
	\input{Chapters/EventReconstruction}
	\input{Chapters/DataAnalysis}
	\input{Chapters/ResultsAndInterpretations}
	\input{Chapters/MTD}

	\end{linenumbers}
%	\printbibliography	
	\bibliographystyle{plain}
	\bibliography{myref}
\end{document}


       
